The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine Cell as Calibrators\altaffilmark{1}

### 2015-07-31 simulation/ms.tex
First skeleton for simulation draft.

% Telluric modeling in Keck/HIRES iodine spectra

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data and Data Analysis Tools}\label{sec:data}

Introduction to Keck/HIRES CPS data, data reduction, Doppler code. Our
adoption of Doppler code.

Introduction to the standard star(s) in this paper?

ZZZ Table: standard star stellar properties? esp. coordinates to
highlight BC ranges?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Effects of Telluric Lines}\label{sec:effects}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Data}

This is where TERRASPEC got introduced.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{On-Sky Data}

Should this be the first?

@@

- RV vs. year/time, RV vs. BC

- RV from chunks with and without telluric lines, vs. BC

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Where and How Telluric Lines Enter the Data}

Should this subsection be moved to the first?
It enters the epoch data as well as the empirically derived stellar template.

- fitting plots showing data (with telluric highlighted) and DSST
(tellurics highlighted) and the mismatch

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Correcting for the Effects of Telluric Lines}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Masking out the Telluric Lines}

ZZZ Plot:

- Illustration of choice of mask

- RV vs. BC before and after for all, telluric, and non-telluric chunks

- simulation results showing no aliases introduced by masking

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Removing the Telluric Contamination from Stellar Templates}

ZZZ Plot:

- selected chunk before and after cleaning

- ?RV vs. BC using cleaned template, no masking, single mask?, double mask?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Modeling Telluric Lines in the Star$+$Iodine Spectra}

ZZZ Plot:

- RV vs. BC using cleaned template plus full telluric modeling

- RV vs. BC using cleaned template plus full modeling plus some masking?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results for A Different RV Standard Star}

I think this is a must! At least one more star, hopefully two.

@@

Gaussian processes!

>>>>

% Effects of telluric lines, as demonstrated via simulation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}\label{sec:method}

Introduction to Keck/HIRES CPS data,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Keck/HIRES Spectra}

- comparison between simulated and observed Keck/HIRES spectra: blaze,
and zoom in.

- comparison between SME stellar template and empirical, deconvolved
template.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Injection of Telluric Lines}

Description of TERRASPEC.

@@

- simulated observation and template with injected tellurics,
overplotted with clean simulated spectra, which would also demonstrate
that due to BC, lines will pull on each other.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction of Radial Velocities}

Introduction to Doppler code and relevant adoption part for the
simulation.

How the end product RVs are computed (vanking, or other weighting schemes).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of Telluric Lines on RV Precision}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Remedies and Their Effectiveness}

@@

- demonstration of effectiveness and ineffectiveness of double masking.

- demonstration of effectiveness of a clean template and forward
modeling tellurics.

- demonstration of precision required for modeling tellurics, and
maximum tolerance for template `cleaness'.

@@

Work on actual observations!
